---
title: "AACR Feedback Report"
output: 
  pdf_document:
    includes:
      in_header: header.tex
---

```{r,echo=FALSE,results='hide',warning=FALSE,message=FALSE,cache=FALSE}
library(knitr)
library(ggplot2)
library(igraph)
library(stringr)
library(RColorBrewer)
library(xtable)
library(extrafont)
library(tables)
library(caret)
library(pander)

opts_chunk$set(cache=FALSE,echo=FALSE)
```

# Student Response Scoring
## Rubric Level Distribution and Description

**QUESTION: `r params$questionText`**

For this question, your students fall into `r length(params$groupLevels)` `r params$groupType`s. Students with similar ideas fall into the same `r params$groupType`. The `r length(params$groupLevels)` `r params$groupType`s and the percentage of students in each `r params$groupType` are shown in the figure below.

```{r,echo=FALSE,fig.height=4,message=FALSE,warning=FALSE}
makeTypedScoringPlot(params,static=TRUE)
```

<br>

```{r,echo=FALSE,comment=NA,results='asis',cache=FALSE}
print(kable(params$questionRubric[,c("Rubric Level","Description")],caption="Item Rubric"))
```

<br>

## Scoring by Rubric Bin and Associated Probability

```{r,results='asis'}
nGroups <- length(params$groupLevels)
tmpRBG <- params$responseByGroup[1,seq(1,2*nGroups,2)]

tmpRBG <- t(tmpRBG)
colnames(tmpRBG) <- "Example Response"

pander(tmpRBG,caption=paste("Example Response of Each",params$groupType))


#nGroups <- length(groupLevels)
#tmpRBG <- params$responseByGroup[1,seq(1,2*nGroups,2)]
#t2 <- xtable(tmpRBG,caption=paste("Example Response of Each",params$groupType))
#if(ncol(tmpRBG)>4){
#        align(t2) <- paste0(c("l",rep(paste0("p{",floor(20/ncol(tmpRBG)),"cm}"),ncol(tmpRBG))),collapse="")
#        print(t2,include.rownames=FALSE,comment=FALSE,floating.environment='sidewaystable',caption.placement="top")
#}else{
#        align(t2) <- paste0(c("l",rep(paste0("p{",floor(15/ncol(tmpRBG)),"cm}"),ncol(tmpRBG))),collapse="")
#        print(t2,include.rownames=FALSE,comment=FALSE,caption.placement="top")
#}
```

\clearpage

# Lexical Analysis
## N-gram Overabundance by Rubric Level

The n-gram overabundance provides a measure of the relative prevalence of a n-gram in a the set of resposes texts in a rubric bin. Specifically, overabundance measures the frequency of a n-gram in the response texts of a given rubric bin with respect to the full set of responses. An overabundance of 0.5 indicates that the n-gram appears 50% more frequently in the responses of the specified rubric bin that it does in the overall set of responses. A value of -0.25 means that the n-gram occurs 25% less often in the relevant rubric bin and than in the overall set.  

```{r,results='asis'}
t3 <- xtable(head(params$oAbDF,20),caption=paste("Overabundance of most frequent n-grams by",params$groupType))
align(t3) <- c("l",rep(">{\\raggedright}X",(ncol(params$oAbDF)-1)),"X")
print(t3,include.rownames=FALSE,comment=FALSE,caption.placement='top',
      tabular.environment="tabularx",width="\\textwidth", table.placement="!h")
```

$$ Overabundace = \frac{\frac{N(term|score)}{N(score)}-\frac{N(term)}{N}}{\frac{N(term)}{N}}$$

\clearpage

## Overabundant N-gram Web Diagrams

The web diagrams shown here display the frequency and co-occurence rates of the most overabundant n-grams in each rubric bin. The circular node symbols display the frequency of n-gram occurence as a fraction of responses scored in the rubric bin which contain a given n-gram. The lines connecting the nodes indicate the frequency for which the two connected n-grams appear together as a fraction of responses in the rubric bin.


```{r,echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
for(gLevel in params$wdMenuList){
        makeWebDiagram(params,values,gLevel,inset=-0.07)
        
        cat("\n\n")
}
```

\clearpage

## N-gram Correlation Maps

The following correlation maps show the most common n-grams for each rubric bin and their mutual correlations represented as an network graph. Each n-gram is displayed as a node, with highly correlated n-grams being connected with lines. The thicker the line connecting two n-grams the stronger they are correlated in the rubric bins response set. Highly correlated groups or clusters of n-grams represent common phrases, sentences, and concepts appearing in student responses.

```{r,echo=FALSE,message=FALSE,warning=FALSE}
probThreshold <- 0
# corThreshold <- 0.3
maxMinFreq <- round(0.3*nrow(values$docTermMat))
minNumTerms <- 5
maxNumTerms <- 25

for(gLevel in params$wdMenuList){
        rubricLevelIndex <- values$predict[[1]]$rubricLevel==gLevel &
                values$predict[[1]]$probability>probThreshold
        dtmTmp <- values$docTermMat[rubricLevelIndex,]
        minFreq <- ifelse(length(findFreqTerms(dtmTmp,lowfreq = 15))>minNumTerms,15,findMinFreq(dtmTmp))
        minFreq <- ifelse(length(findFreqTerms(dtmTmp,lowfreq = minFreq))>maxNumTerms,findMinFreq(dtmTmp,maxNumTerms),minFreq) #find maximum minimum frequency
        corThreshold <- params$mapControlLimits[[as.numeric(gLevel)]][4]
        makeTermMap(dtmTmp,minFreq,corThreshold)
        title(names(params$wdMenuList[gLevel]))
        cat("\n\n")
}
```

\clearpage

# Training Set Scoring Model Performance
## Scoring Model Cross Validation

**Please Note:** The data in the following section refers to the cross validation of the scoring model training set. This data does not refer to the data uploaded and scored in the production of this Instructor Feedback Report. It is presented to give the background information on the performance of the `r params$questionText` item scoring model.

Training set size per fold: `r paste0("N = ",values$trainLength)`  
Total number of scored responses: `r values$scoreLength`   

### Confusion Matrix

```{r,echo=FALSE,comment=NA,message=FALSE,results='asis'}
cat("\\begin{center}")
latex(as.tabular(values$cvOut[[1]]$table))
cat("\\end{center}")
```

### Overall Statistics

```{r,echo=FALSE,comment=NA,results="asis",message=FALSE}
digitsFmt <- 3
tmp <- values$cvOut[[1]]$overall
dfOut <- data.frame(
        Kappa=round(tmp["Kappa"],digitsFmt),
        Accuracy=round(tmp["Accuracy"],digitsFmt),
        "Accuracy 95% CI"=paste(round(tmp["AccuracyLower"],digitsFmt),"-",round(tmp["AccuracyUpper"],digitsFmt)),
        "No Information Rate"=round(tmp["AccuracyNull"],digitsFmt),
        "P-Value [Acc > NIR]"=signif(tmp["AccuracyPValue"],digitsFmt),
        "McNemar's Test P-Value"=signif(tmp["McnemarPValue"],digitsFmt),check.names = FALSE,row.names = NULL
)
print(kable(t(dfOut)))
cat("\n")
```

### By Rubric Bin

```{r,echo=FALSE,comment=NA,results="asis",message=FALSE}
print(kable(t(values$cvOut[[1]]$byClass),digits=digitsFmt))
cat("\n")
```

