---
title: "AACR Feedback Report"
output: 
  pdf_document:
    includes:
      in_header: header.tex
---

```{r,echo=FALSE,results='hide',warning=FALSE,message=FALSE,cache=FALSE}
library(knitr)
library(ggplot2)
library(igraph)
library(stringr)
library(RColorBrewer)
library(xtable)
library(extrafont)
library(tables)
library(caret)
library(tables)

opts_chunk$set(cache=FALSE,echo=FALSE)
```


# Student Response Scoring
## Rubric Level Distribution and Description

**QUESTION: `r questionText`**

For this question, your students fall into `r length(params$groupLevels)` `r params$groupType`s. Students with similar ideas fall into the same `r params$groupType`. The `r length(params$groupLevels)` `r params$groupType`s and the percentage of students in each `r params$groupType` are shown in the figure below.

```{r,echo=FALSE,fig.height=4,message=FALSE,warning=FALSE}

makeBinaryScoringPlot(params,static=TRUE)

```

<br>

```{r,echo=FALSE,comment=NA,results='asis',cache=FALSE}
print(kable(params$questionRubric[,c("Rubric Level","Description")],caption="Item Rubric"))

```

\clearpage


## Co-occurence of Rubric Levels
### Co-occurence Web Diagram
The circular nodes in this plot correspond with the item rubric bins. The edges (lines) connecting the nodes correspond to co-occurence rates bewtween the rubric bins in the scored sample. In this diagram both nodes and edges are scaled in size and color to represent the range of rubric bin and co-occurence frequencies as shown in the figure keys.

```{r,echo=FALSE,message=FALSE,warning=FALSE,results='asis',fig.height=3.5}
makeCooccurWD(params,values,inset=-0.07)
```


### Co-occurence Frequencies

The co-occurence freqencies displayed in the figures below describe the fraction of student responses which have been score for the rubric bin appearing in the title that also are scored for the rubric bins listed on the vertical axis.

```{r,echo=FALSE,message=FALSE,warning=FALSE,results='asis',fig.height=3.5}
for(gLevel in params$wdMenuList){
        print(makeCooccurFreqPlot(values,params,as.numeric(gLevel),static=TRUE))
        
        
        cat("\n\n")

}
```


\clearpage

